Adaptive group-regularized logistic elastic net regression Supplementary material

### 2019-03-07 docs/supplement.Rnw
all barplots, auc, and briers figures in supplement

  \section{Application to RNAseq in lymph node cancer}
  In addition to the results presented in Section [! section ref here] of the 
  MD, we compared \texttt{gren} to the sparse group lasso (\texttt{SGL}) by 
  \cite{simon_sparse-group_2013} and the group exponential lasso (\texttt{gel}) 
  by \cite{breheny_group_2015}. The original group lasso methods are not 
  designed to deal with overlapping groups, so in addition to using the versions
  that allow for overlapping groups, we 
  cross-tabulated the two co-data partitions to create one paritioning with 25 
  groups for \texttt{cMCP} and \texttt{gel}.
  We use $\alpha \in \{0.05, 0.5, 0.95 \}$ for the
  methods that require this extra tuning parameter. The AUCs calculated on the
  validation set are presented in Figure 
  \ref{fig:lines_rnaseq_lymph_node_metastasis_res1_auc}
<<lines_rnaseq_lymph_node_metastasis_res1_auc, fig.cap="Estimated AUC for the lymph node cancer example.", out.width="100%", fig.asp=1>>=
@

@@

	To estimate performance measures AUC and BSS, we split the data into 120 
	training instances and 54 test instances. 
	The training data is used to fit the models, while the test data
	is used to estimate the performance measures on. We included the different 
	co-data types seperately and combined, which resulted in the estimated 
	multipliers and performance measures presented in Figure 
	\ref{fig:barplot_lines_metabolomics_alzheimer_res5_auc}.
<<barplot_lines_metabolomics_alzheimer_res5_auc, fig.cap="Results for the alzheimer example with (a) the estimated penalty multipliers for the quality score, (b) the estimated penalty multipliers for the network degree, (c) the estimated AUC, and (d) the estimated Brier skill score.", out.width="100%", fig.asp=1>>=
@

@@

<<barplots_micrornaseq_cervical_cancer_res1_auc, fig.cap="Estimated penalty multipliers for conservation status co-data", out.width="50%", fig.asp=2/3>>=
@

<<lines_micrornaseq_cervical_cancer_res1_auc, fig.cap="Cross-validated AUC in cervicl cancer example", out.width="50%", fig.asp=1>>=
@

  \section{Choice of \texorpdfstring{$\alpha$}{alpha}}	
	Choice of $\alpha$ does matter in Figure 
	\ref{fig:lines_colorectal_lymph_node_gren_auc}.
<<lines_colorectal_lymph_node_gren_auc, fig.cap="Estimated AUC for gren in the (a) colorectal cancer example and the (b) lymph node metastasis example.", out.width="100%", fig.asp=1/2>>=
@

>>>>

  \section{Application to RNAseq in lymph node cancer}
  In addition to the results presented in Section [! section ref here] of the 
  MD, we compared \texttt{gren} to the sparse group lasso (\texttt{SGL}) by 
  \cite{simon_sparse-group_2013} and the group exponential lasso (\texttt{gel}) 
  by \cite{breheny_group_2015}. The original group lasso methods are not 
  designed to deal with overlapping groups, so in addition to using the versions
  that allow for overlapping groups, we 
  cross-tabulated the two co-data partitions to create one paritioning with 25 
  groups for \texttt{cMCP} and \texttt{gel}.
  We use $\alpha \in \{0.05, 0.5, 0.95 \}$ for the
  methods that require this extra tuning parameter. The AUCs and Brier skill 
  scores calculated on the
  validation set are presented in Figures 
  \ref{fig:lines_rnaseq_lymph_node_metastasis_res1_auc}--
  \ref{fig:lines_rnaseq_lymph_node_metastasis_res1_briers}
<<lines_rnaseq_lymph_node_metastasis_res1_auc, fig.cap="Estimated AUC for the lymph node cancer example.", out.width="100%", fig.asp=1>>=
@

<<lines_rnaseq_lymph_node_metastasis_res1_briers, fig.cap="Estimated Briers skill score for the lymph node cancer example.", out.width="100%", fig.asp=1>>=
@

@@

	To estimate performance measures AUC and Briers skill score, we split the data
	into 120 training instances and 54 test instances. 
	The training data is used to fit the models, while the test data
	is used to estimate the performance measures on. This resulted in the 
	estimated multipliers and performance measures presented in Figures 
	\ref{fig:barplot_metabolomics_alzheimer_res1}--
	\ref{fig:lines_metabolomics_alzheimer_res1_briers}.
<<barplot_metabolomics_alzheimer_res1, fig.cap="Estimated penalty multiplies for the (a) quality score and the (b) network degree in the alzheimer example.", out.width="100%", fig.asp=1/2>>=
@

<<lines_metabolomics_alzheimer_res1_auc, fig.cap="Estimated AUC for the alzheimer example.", out.width="100%", fig.asp=1>>=
@

<<lines_metabolomics_alzheimer_res1_briers, fig.cap="Estimated Brier skill score for the alzheimer example.", out.width="100%", fig.asp=1>>=
@

@@

<<barplot_micrornaseq_cervical_cancer_res1, fig.cap="Estimated penalty multiplies for conservation status in cervical cancer example.", out.width="50%", fig.asp=1>>=
@

<<lines_micrornaseq_cervical_cancer_res1_auc, fig.cap="Cross-validated AUC in cervical cancer example", out.width="100%", fig.asp=1>>=
@

<<lines_micrornaseq_cervical_cancer_res1_briers, fig.cap="Cross-validated Brier skill score in cervical cancer example", out.width="100%", fig.asp=1>>=
@
